15th International Satisfiability Modulo Theories Competition (SMT-COMP 2021): Rules and Procedures

### 2021-05-07 rules/rules21.tex
updating division split for all tracks

The rest of this document, revised from the previous
version,\footnote{Earlier versions of this document include
  contributions from Clark Barrett, Roberto Bruttomesso, David Cok,
  Sylvain Conchon, David D{\'e}harbe, Morgan Deters, Alberto Griggio,
  Liana Hadarean,
  Matthias Heizmann, Aina Niemetz, Albert Oliveras, Giles Reger, Aaron Stump,
  and Tjark Weber.}  describes the rules and competition procedures for
SMT-COMP~2021.
%
As in previous years, we have revised the rules slightly.  Some rule
changes in 2021 are designed to not overly punish solvers producing
syntactically wrong output, by treating those outputs as unknown and
not as unsoundness.  Moreover, we added more divisions to the model
validation track.
%
The principal changes from the previous competition rules are the following:
\begin{itemize}
  \item {\bf \maintrack.} Previously, every logic in the \maintrack was its own
  division.  There are currently over 60 logics in SMT-LIB, which makes a short
  summary of the results impossible.  On the other hand the competition-wide
  scoring does a comparison between solvers that cannot be sensibly compared as
  they support completely disjoint logics. To get a better overview, this year
  we have in the \maintrack divisions combining related logics, thus reducing
  the number of divisions and obtaining more manageable and meaningful results.
  Rather than logics, solvers will declare the divisions they enter in the
  \maintrack. They will be ranked by the number of benchmarks they solve across
  all logics in the divisions entered.
  \begin{itemize}
    \item Quantifier-free divisions:
    \begin{itemize}
      \item QF\_Equality\\
Logics: QF\_UF, QF\_AX, QF\_DT, QF\_UFDT
\item QF\_Equality+LinearArith\\
Logics: QF\_ALIA, QF\_AUFLIA, QF\_UFLIA, QF\_UFLRA, QF\_UFIDL
\item QF\_Equality+NonLinearArith\\
Logics: QF\_UFNRA, QF\_UFNIA, QF\_ANIA, QF\_AUFNIA
\item QF\_Equality+Bitvec\\
Logics: QF\_ABV, QF\_UFBV, QF\_AUFBV
\item QF\_Equality+Bitvec+Arith\\
Logics: QF\_AUFBVLIA, QF\_AUFBVNIA, QF\_UFBVLIA
\item QF\_LinearIntArith\\
Logics: QF\_LIA, QF\_LIRA, QF\_IDL
\item QF\_LinearRealArith\\
Logics: QF\_LRA, QF\_RDL
\item QF\_Bitvec\\
Logics: QF\_BV
\item QF\_FPArith\\
Logics: QF\_FP, QF\_UFFP, QF\_FPLRA, QF\_BVFP, QF\_ABVFP, QF\_AUFBVFP, QF\_BVFPLRA, QF\_ABVFPLRA
\item QF\_NonLinearIntArith\\
Logics: QF\_NIA, QF\_NIRA
\item QF\_NonLinearRealArith\\
Logics: QF\_NRA
\item QF\_Strings\\
Logics: QF\_S, QF\_SLIA, QF\_SNIA

@@

  \item {\bf \mvaltrack.}  Last year's competition introduced the experimental
    divisions QF\_IDL, QF\_RDL, QF\_LIA, QF\_LRA, QF\_LIRA in the
    model validation track.  This year these will no longer be experimental.
    In addition, new experimental divisions QF\_UF, QF\_UFBV,
    QF\_UFIDL, QF\_UFLIA, QF\_UFLRA will be added.

  \rationale{There were only small issues with these divisions, so there is no
    reason to keep it experimental. For the new divisions, as before, given the
    inconsistencies across different model producing solvers, we proceed in an
    experimental fashion to push for model standardization.}

@@

For each track and division, we compute a division score based on the parallel
performance of a solver (the \emph{parallel division score}).  For the
\maintrack, \ucoretrack and \mvaltrack we also compute a division
score based on the sequential performance of a solver (the \emph{sequential
division score}).  Additionally, for the \maintrack, we further determine three
additional scores based on parallel performance: The \emph{24-second score}
will reward solving performance within a time limit of 24 seconds (wall clock
time), the \emph{sat score} will reward (parallel) performance on satisfiable
instances, and the \emph{unsat score} will reward (parallel) performance on
unsatisfiable instances.
%
Finally, for the \maintrack all the above scores, in divisions composed by more
than one logic, will be presented not only for the overall division but also for
each logic composing the division.

>>>>

The rest of this document, revised from the previous
version,\footnote{Earlier versions of this document include
  contributions from Clark Barrett, Roberto Bruttomesso, David Cok,
  Sylvain Conchon, David D{\'e}harbe, Morgan Deters, Alberto Griggio,
  Liana Hadarean,
  Matthias Heizmann, Aina Niemetz, Albert Oliveras, Giles Reger, Aaron Stump,
  and Tjark Weber.}  describes the rules and competition procedures for
SMT-COMP~2021.
%
As in previous years, we have revised the rules slightly.  Some rule
changes in 2021 are designed to not overly punish solvers producing
syntactically wrong output, by treating those outputs as unknown and
not as unsoundness.  Moreover, we added more divisions to the model
validation track.
%
The principal changes from the previous competition rules are the following:
\begin{itemize}
  \item {\bf Divisions now may contain more than one logic.} Previously, every
  division was comprised of a single logic. There are currently over 60 logics
  in SMT-LIB, which makes a short summary of the results impossible.  On the
  other hand the competition-wide scoring does a comparison between solvers that
  cannot be sensibly compared as they support completely disjoint logics. To get
  a better overview, this year divisions will combine related logics, thus
  reducing the number of divisions and obtaining more manageable and meaningful
  results.  Rather than logics, solvers will declare the divisions they
  enter. They will be ranked by the number of benchmarks they solve across all
  logics in the divisions entered.
  \begin{itemize}
    \item Quantifier-free divisions:
    \begin{itemize}
      \item QF\_Equality\\
Logics: QF\_UF, QF\_AX, QF\_DT, QF\_UFDT
\item QF\_Equality+LinearArith\\
Logics: QF\_ALIA, QF\_AUFLIA, QF\_UFLIA, QF\_UFLRA, QF\_UFIDL
\item QF\_Equality+NonLinearArith\\
Logics: QF\_UFNRA, QF\_UFNIA, QF\_ANIA, QF\_AUFNIA
\item QF\_Equality+Bitvec\\
Logics: QF\_ABV, QF\_UFBV, QF\_AUFBV
\item QF\_Equality+Bitvec+Arith\\
Logics: QF\_AUFBVLIA, QF\_AUFBVNIA, QF\_UFBVLIA
\item QF\_LinearIntArith\\
Logics: QF\_LIA, QF\_LIRA, QF\_IDL
\item QF\_LinearRealArith\\
Logics: QF\_LRA, QF\_RDL
\item QF\_Bitvec\\
Logics: QF\_BV
\item QF\_FPArith\\
Logics: QF\_FP, QF\_UFFP, QF\_FPLRA, QF\_BVFP, QF\_ABVFP, QF\_AUFBVFP, QF\_BVFPLRA, QF\_ABVFPLRA
\item QF\_NonLinearIntArith\\
Logics: QF\_NIA, QF\_NIRA
\item QF\_NonLinearRealArith\\
Logics: QF\_NRA
\item QF\_Strings\\
Logics: QF\_S, QF\_SLIA, QF\_SNIA

@@

  \item {\bf \mvaltrack.}  Last year's competition introduced the experimental
  divisions QF\_IDL, QF\_RDL, QF\_LIA, QF\_LRA, QF\_LIRA in the model validation
  track.  This year, the divisions containing these logics will no longer be
  experimental.  In addition, we will add this year new experimental divisions
  QF\_Equality (only with QF\_UF benchmarks), QF\_Equality+LinearArith (only with
  QF\_UFIDL, QF\_UFLIA, and QF\_UFLRA benchmarks), and QF\_Equality+Bitvec (only with
  QF\_UFBV benchmarks).

  \rationale{There were only small issues with last year's divisions, so there is no
    reason to keep them experimental. For the new divisions, as before, given the
    inconsistencies across different model producing solvers, we proceed in an
    experimental fashion to push for model standardization.}

@@

For each track and division, we compute a division score based on the parallel
performance of a solver (the \emph{parallel division score}).  For the
\maintrack, \ucoretrack and \mvaltrack we also compute a division
score based on the sequential performance of a solver (the \emph{sequential
division score}).  Additionally, for the \maintrack, we further determine three
additional scores based on parallel performance: The \emph{24-second score}
will reward solving performance within a time limit of 24 seconds (wall clock
time), the \emph{sat score} will reward (parallel) performance on satisfiable
instances, and the \emph{unsat score} will reward (parallel) performance on
unsatisfiable instances.
%
Finally, in divisions composed by more than one logic, all the above scores will
be presented not only for the overall division but also for each logic composing
the division.
